%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Assignment
% LaTeX Template
% Version 2.0 (12/1/2019)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Frits Wenneker
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{scrartcl} % Font size

\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\title{	
	\normalfont\normalsize
	\textsc{LVS Ascot}\\ % Your university, school and/or department name(s)
	\vspace{25pt} % Whitespace
	\rule{\linewidth}{0.5pt}\\ % Thin top horizontal rule
	\vspace{20pt} % Whitespace
	{\huge Fantastic Beasts: The Crimes of Grindelwald}\\ % The assignment title
	\vspace{12pt} % Whitespace
	\rule{\linewidth}{2pt}\\ % Thick bottom horizontal rule
	\vspace{12pt} % Whitespace
}

\author{\LARGE Max Sepulveda} % Your name

\date{\normalsize\today} % Today's date (\today) or a custom date

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	FIGURE EXAMPLE
%----------------------------------------------------------------------------------------

\section{Book summary}

Fantastic Beasts: The Crimes of Grindelwald was written by J. K. Rowling. The plot follows Newt Scamander and Albus Dumbledore as they attempt to take down the dark wizard Gellert Grindelwald, while facing new threats in a more divided world of wizards.

%------------------------------------------------

\section{Chapter 1}

Newt Scamander is a young wizard which has written a book about rare beasts which not many people know about.

The chapter starts with him at the Ministry of magic waiting for his session where he will try to lift his ban from travelling internationally.

The ministry of Magic gives him the chance to lift the ban only if he joined the Ministry, in the same department as his brother. This meant for Newt to become an auror and thus he had to hunt down Credence.

Credence is a young boy, a very powerful wizard, he is looking for his mother. As the Ministry fears his power they want to put him in jail or if necessary kill him.

Newt refuses to take part of this and his appeal is declined.

Later we see Newt in his house's basement where he keep all of his beasts are kept, and he takes care of them. A sound is heard, he goes upstairs discovering Queenie and Jacob both friends of Newt.

After discovering that Queenie had put Jacob under a love enchantment Newt removes it. Jacob seems upset, Queenie gets angry and escapes to France searching for her sister. She is in there searching for Credence.

Now Newt and Jacob must go to France. Jacob will go because even though he was upset he still loves Queenie and Newt because he wants to see Queenies' sister Tina.

%----------------------------------------------------------------------------------------

\begin{thebibliography}{99}

\bibitem{latexcompanion} 
Rowling, Joanne Kathleen. 
\textit{Fantastic Beasts: The crimes of Grindelwald - the original screenplay}. 
Pottermore Publishing, 2018.

\end{thebibliography}

\end{document}
